Title

### 2012-07-10 inc/liouvilles_theorem/liouvilles_theorem.tex
insert commentary from JAP paper to relevant places
A little more reoganization related to splitting the AG model chapter in two. Futher I have started an introduction to the extension chapter
highlight that \Gamma^2 constants are indeed constants, evaluated at time t=0

\subsection{Implications of Liouville's Theorem}

@@

Not only is this an interesting result, but it can be both instructive and computationally useful.
By rewriting \ref{eq:define_big_gamma} as $\eta_{\alpha} = \Gamma_{\alpha}^2 / \sigma_{\alpha}$ and substituting into \ref{eq:ag_original}.
\begin{subequations} \label{eq:ag_big_gamma}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)
\end{gather}
\end{subequations}
these four equations now contain all of the information previously contained in six. Having fewer equations, and fewer mathematical operations, makes this set of equations much less computationally intensive.
Further, now one can see that these $\Gamma$ constants can be thought of as some minimum/intrinsic action of the pulse. 
This will become more apparent when in future sections
%TODO include internal reference
it is shown that at the focal point of a lens, $\gamma_{\alpha}$ goes through zero.

>>>>

\section{Implications of Liouville's Theorem}

@@

Not only is this an interesting result, but it can be both instructive and computationally useful.
By rewriting \ref{eq:define_big_gamma} as $\eta_{\alpha} = \Gamma_{\alpha}^2 / \sigma_{\alpha}$, evaulating at some time (presumably $t=0$) and substituting into \ref{eq:ag_original}.
\begin{subequations} \label{eq:ag_big_gamma}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2(0) + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)
\end{gather}
\end{subequations}
these four equations now contain all of the information previously contained in six.
Having fewer equations, and fewer mathematical operations, makes this set of equations much less computationally intensive.
Further, now one can see that these $\Gamma$ constants can be thought of as some minimum/intrinsic action of the pulse. 
This will become more apparent when in future sections
%TODO include internal reference
it is shown that at the focal point of a lens, $\gamma_{\alpha}$ goes through zero.

In the transverse dimension, this is consistent with the definition of `coherent fluence' employed by Reed et al.\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the spatial emittance of an electron beam\cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
